Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/conclusion.tex

In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy in the abstract \ac{MDP}. This approach is appealing for two reasons. First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}. Second, since the state-aggregation criteria are relaxed to approximate equality, methods that employ these techniques are able to tune the aggressiveness of state aggregation all the while incurring bounded error. We evaluate our approaches empirically on four different \acs{MDP}, providing visuals of the compression, as well as displaying the relationship between $\epsilon$ and the degree of compress, as well as the value of the abstract policy. We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.

There are many directions for future work. First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting. \citeauthor{ortner2013adaptive} previously proposed this strategy by combining the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}, and are curious how this strategy will fair under the proposed approximate abstraction families introduced in this paper. Learning these abstraction functions also poses interesting implications for the exploration problem. If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,

@@

% Summary

% Future Work
\begin{enumerate}
\item Learning Phi
\begin{itemize}
\item Exploration vs. Exploitation problem is different while trying to learn Phi
\end{itemize}
\item Compressibility
\begin{itemize}
\item Relationship between approximate abstract and compressibility
\end{itemize}
\item POMDP and abstraction
\end{enumerate}

>>>>

% Summary of contributions.
In this work we investigate the aggregation of states on the basis of four classes of approximate criteria, and provide bounds for the value lost when behaving according to the optimal policy in the abstract \ac{MDP}. This approach is appealing for two reasons. First, approximate abstraction relies on criteria that we imagine a planning or learning algorithm to be able to learn without solving the full \ac{MDP}. Second, since the state-aggregation criteria are relaxed to approximate equality, methods that employ these techniques are able to tune the aggressiveness of state aggregation all the while incurring bounded error. We evaluate our approaches empirically on four different \acs{MDP}, providing visuals of the compression, as well as displaying the relationship between $\epsilon$ and the degree of compress, as well as the value of the abstract policy. We provide a code base that provides implementations to abstract, visualize, and evaluate an arbitrary MDP to promote further investigation into approximate abstraction.

% Future work.
There are many directions for future work. First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}. Learning abstraction functions online also has interesting implications for the exploration problem. If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,

@@
